Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-12 implementation.tex
Revised section 3.2.1
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1043 ccdd05d5-56c1-461a-bf98-85f6876523b4
Revised section 3.2
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1044 ccdd05d5-56c1-461a-bf98-85f6876523b4

\subsubsection{Decimation}

The whitened detector data is reduced to successively
lower sample rates by decimation. Decimation involves applying an anti-aliasing
filter to the data, and then down-sampling by deleting samples.  We use a
192-tap \fir\ decimator provided by \gstreamer{}'s {\tt audioresample}
element.  The detector data is provided at every power-of-two sample rate
required by the template time slices described in \eqref{eq:time-slices}. Next,
these decimated data streams are fed into parallel \fir\ filter banks.

\subsubsection{\fir\ filters}

The \fir\ filtering is implemented using a \gstlal\ element called {\tt
lal\_firbank}, which produces $N$ channels of filter output from an $N\times M$ matrix of
\fir\ filter coefficients, representing the \SVD{} basis filters in our application.  This element is used in parallel branches in the
pipeline to implement the \SVD\ basis filters in each time
slice.  Rather than implement the time-sliced templates as zero-padded \fir\
filters as described in \eqref{eq:time-slices} we instead implement them as shorter
filters that contain only the nonzero samples.  Adding the appropriate time
offset to the filter output later in the pipeline makes up for the lack of
explicit zero-padding.

\subsubsection{Reconstruction}

From the outputs of the \SVD\ basis filters, we form the partial \SNR{}s for each time 
slice by multiplying by the reconstruction matrices.  This is accomplished by connecting 
the \texttt{gstlal} element \texttt{lal\_matrixmixer} to the output of
\texttt{lal\_firbank}.

\subsubsection{Interpolation}

In order to form the early-warning output from each time slice, we have to add
the partial \SNR\ to the early-warning output from the subsequent time slices.
If the next time slice does not have the same sample rate, its output must
first be interpolated.  This is done using the same \gstreamer\ element as was
used for decimation, {\tt audioresample}.

\subsubsection{\SNR\ accumulation}

>>>>

\paragraph{Decimation}

The whitened detector data is reduced to successively
lower sample rates by decimation. Decimation involves applying an anti-aliasing
filter to the data, and then down-sampling by deleting samples.  We use a
192-tap \fir\ decimator provided by \gstreamer{}'s {\tt audioresample}
element.  The detector data is provided at every power-of-two sample rate
required by the time slices described in \eqref{eq:time-slices}.  At this point,
the \gstreamer\ pipeline splits into several parallel branches to handle each
time slice.  Next, these decimated data streams are fed into parallel \fir\ filter banks.

\paragraph{Basis filters}

The basis filters are implemented using a \gstlal\ element called {\tt
lal\_firbank}, which provides a single input, multiple output bank of \fir\ filters
from a matrix of filter coefficients.  Several instances of {\tt lal\_firbank}
execute in parallel to handle each of the time slices.  Filter coefficients are taken
from the nonzero samples of the time slices in equation~\eqref{eq:time-sliced-templates},
with the zero-padding effectively accomplished by appropriate delays.

\paragraph{Reconstruction}

From the outputs of the \SVD\ basis filters, we form the partial \SNR streams for
each time  slice by multiplying by the reconstruction matrices.  This is accomplished
with the \texttt{gstlal} element \texttt{lal\_matrixmixer}.

\paragraph{Interpolation}

In order to form the early-warning output from each time slice, we have to add
the partial \SNR\ to the early-warning output from the subsequent time slices.
If the next time slice does not have the same sample rate, its output must
first be interpolated.  The \gstreamer\ element {\tt audioresample} is used here.

\paragraph{\SNR\ accumulation}
